Calendar-based graphics for visualising people's daily schedules

### 2017-07-06 main.Rmd
added more to scales

## Grid construction

@@

One of the advantages using glyphs over heatmaps is evident in easily enabling scales on different temporal scales. All of the line glyphs shown above are drawn on the global scale so that it makes the magnitudes comparable over all the period. On the other hand, some sub-series of small magnitudes yet worth-noting shapes possibly become invisible whilst embedded in the overall picture. The individual scale or something else, as a result, complements the calendar-based visualisation in general.

There are other three types of scales in addition to the global scale: individual scales regardless of days, conditional on weekdays, and conditional on days of a month.

>>>>

## Grid construction
\label{sec:grid}

@@

Section \ref{sec:grid} discusses the implementation applied to the fixed scale which is using the whole range of all the data values. In addition to the fixed scale (\code{fixed}), the remaining options include free scale on all the days (\code{free}), day of the week only (\code{free_wday}), and day of the month only (\code{free_mday}) for different comparisons.

Grouping the cells according to the common days give rise to these scales. The minimums and maximums computed for every $(i, j)$ together with every $(m, n)$ allow for individual scale over all the single days. Similarly, $j$ indexing day of the week is bundled to determine the scales on days of a week, and $g$ representing the day in the month is for the scales on days of a month.

All the figures shown before are drawn on the fixed scale so that it makes the magnitudes comparable over the whole period of time. On the other hand, some sub-series of small magnitudes yet worth-noting shapes possibly become invisible whilst embedded in the overall picture. These sorts of scales, as a result, complements the calendar-based visualisation in general. (NEED FIGURES)

### 2017-07-06 main.tex
added more to scales

@@

One of the advantages using glyphs over heatmaps is evident in easily
enabling scales on different temporal scales. All of the line glyphs
shown above are drawn on the global scale so that it makes the
magnitudes comparable over all the period. On the other hand, some
sub-series of small magnitudes yet worth-noting shapes possibly become
invisible whilst embedded in the overall picture. The individual scale
or something else, as a result, complements the calendar-based
visualisation in general.

There are other three types of scales in addition to the global scale:
individual scales regardless of days, conditional on weekdays, and
conditional on days of a month.

>>>>

\label{sec:grid}

@@

Section \ref{sec:grid} discusses the implementation applied to the fixed
scale which is using the whole range of all the data values. In addition
to the fixed scale (\code{fixed}), the remaining options include free
scale on all the days (\code{free}), day of the week only
(\code{free_wday}), and day of the month only (\code{free_mday}) for
different comparisons.

Grouping the cells according to the common days give rise to these
scales. The minimums and maximums computed for every \((i, j)\) together
with every \((m, n)\) allow for individual scale over all the single
days. Similarly, \(j\) indexing day of the week is bundled to determine
the scales on days of a week, and \(g\) representing the day in the
month is for the scales on days of a month.

All the figures shown before are drawn on the fixed scale so that it
makes the magnitudes comparable over the whole period of time. On the
other hand, some sub-series of small magnitudes yet worth-noting shapes
possibly become invisible whilst embedded in the overall picture. These
sorts of scales, as a result, complements the calendar-based
visualisation in general. (NEED FIGURES)
